---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grangeR

The goal of `grangeR` is to provide---in a single place---several utilility functions often used 
in the research of the [Grange Lab](https://jimgrange.github.io/). These range from general helper functions to full plotting functions.

## Installation

You can install the development version of `grangeR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JimGrange/grangeR")
```

## Implemented Functions

### Plotting
* `get_cdf()`: Produces cumulative density function (CDF) plots for response time experimental data. Defective CDFs (i.e., quantiles scaled by accuracy) can also be produced.
* `get_caf()`: Produces conditional accuracy function (CAF) plots for response time and accuracy experimental data. 

```{r fig.width=6}
library(grangeR)
data <- grangeR::task_switching

cdf_plot <- get_cdf(data = data, 
                    id_var = "id", 
                    conditions = c("response_set_sequence", 
                                   "stimulus_set_sequence",
                                   "compatibility"), 
                    defective = TRUE)
cdf_plot$plot
```

